Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-10 report/report.tex
Update todo
Add note about the percentages of road that could not be corrected
Updated turning function example image with key features

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_turn_function}
    \caption{An example of the turning function of a polygon.}
    \label{fig:turning-function}
\end{figure}

@@

Table \ref{table:road-collision} shows the statistics of the collision study, and the number of roads, number of edges and total edge length that showed intersections with other features before road extrusion, by road category.
For footpaths in particular, it was shown that 12.05\% of all roads collide with some other feature after extrusion to the minimum width.
The same was shown to be true for 0.11\% of the road polyline edges and 0.09\% of the total road length.
Table \ref{table:road-collision-corrected} shows the remaining roads, edges and total edges length whose intersections with other features could not be resolved by geometrical translation of a distance smaller than the positional accuracy.

@@

% TODO: Reformat 8.3 to show the suggested algorithms in a list, with figure references
% TODO: Complementary text in the results section
% TODO: Proper citations (Fix links)

% TODO: Figure showing how turning function is calculated from edges and angles
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Algorithm showing the edge projected distance algorithm for the collision study
% TODO: Expand on analysis about Feature overlap

@@

***\% of feautures collide and ***\% of edges.
This means that for each colliding road, on average ***\% of its edges will be intersecting some other feature, thus bearing responsibility for the collision.
In total there are ***\% feautures ***\% edges, meaning that each feature on average is contructed out of *** edges.
Thus the percentage of edges colliding per road is on average ***\%.
The conclusion is that most often, a small part of a road is colliding, and will need correction.
Visual inspection of the cases where roads collide with other features has supported this.

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_turn_function}
    \caption{An example of the turning function of a polygon. The edges, vertices and angle of the initial step of the turning funciton are marked.}
    \label{fig:turning-function}
\end{figure}

@@

Table \ref{table:road-collision} shows the statistics of the collision study, and the number of roads, number of edges and total edge length that showed intersections with other features before road extrusion, by road category.
For footpaths in particular, it was shown that 12.05\% of all roads collide with some other feature after extrusion to the minimum width.
The same was shown to be true for 0.11\% of the road polyline edges and 0.09\% of the total road length.
Table \ref{table:road-collision-corrected} shows the remaining roads, edges and total edges length whose intersections with other features could not be resolved by geometrical translation of a distance smaller than the positional accuracy.
For footpaths this was shown to hold of 0.51\% of all roads, 
The number of road edges and percentage of the total road length that could not be corrected by geometric translation was significantly small.

@@

% TODO: Reformat 8.3 to show the suggested algorithms in a list, with figure references
% TODO: Figure showing how turning function is calculated from edges and angles

% TODO: Proper citations (Fix links)
% TODO: Expand on analysis about Feature overlap

% TODO: Algorithm showing the edge projected distance algorithm for the collision study
% TODO: Figure detailing the steps in the point-matching algorithm

@@

%TODO: Calculations here
***\% of feautures collide and ***\% of edges.
This means that for each colliding road, on average ***\% of its edges will be intersecting some other feature, thus bearing responsibility for the collision.
In total there are ***\% feautures ***\% edges, meaning that each feature on average is contructed out of *** edges.
Thus the percentage of edges colliding per road is on average ***\%.
The conclusion is that most often, a small part of a road is colliding, and will need correction.
Visual inspection of the cases where roads collide with other features has supported this.
